---
title: "Customer Churn Analysis Report"
author: "[Your Name]"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(kableExtra)
```

## Executive Summary

This analysis identifies key factors driving customer churn and provides actionable recommendations for marketing retention strategies.

## 1. Data Overview

```{r data-overview}
customer_data <- read.csv("data/sample_customer_data.csv")
dimensions <- dim(customer_data)
churn_rate <- round(mean(customer_data$churn_status) * 100, 2)

cat("**Dataset:**", dimensions[1], "customers,", dimensions[2], "variables\n")
cat("**Overall Churn Rate:**", churn_rate, "%")
```

## 2. Key Findings

### Churn Distribution
```{r churn-distribution}
ggplot(customer_data, aes(x = factor(churn_status, labels = c("Active", "Churned")))) +
  geom_bar(fill = c("#2E8B57", "#DC143C"), alpha = 0.8) +
  labs(title = "Customer Churn Distribution", x = "Status", y = "Count") +
  theme_minimal()
```

### Contract Type Analysis
```{r contract-analysis}
churn_by_contract <- customer_data %>%
  group_by(contract_type) %>%
  summarise(
    Customers = n(),
    Churn_Rate = paste0(round(mean(churn_status) * 100, 1), "%"),
    Avg_Tenure = round(mean(tenure_months), 1)
  )

kable(churn_by_contract, caption = "Churn Analysis by Contract Type") %>%
  kable_styling(bootstrap_options = "striped")
```

## 3. Strategic Recommendations

1. **Contract Strategy**: Focus on converting month-to-month customers to annual contracts
2. **Pricing Review**: Analyze pricing sensitivity in high-churn segments  
3. **Retention Campaigns**: Target customers with <12 months tenure
4. **Proactive Support**: Reduce support calls through improved self-service

*Report generated on `r Sys.Date()`*